---
title: 'Exercise #3'
author: "Sungho Park (12469817), Jonas Reinhard (Martrikelnummer), ..."
date: "`r Sys.Date()`"
output: pdf_document
subtitle: "Fortgeschrittene Statistische Software für NF - SS 2022/23"
---

## General Remarks

-   You can submit your solutions in teams of up to 3 students.
-   Include all your team-member's names and student numbers
    (Martrikelnummern) in the `authors` field.
-   Please use the exercise template document to work on and submit your
    results.
-   Use a level 2 heading for each new exercise and answer each subtask
    next to it's bullet point or use a new level 3 heading if you want.
-   Always render the R code for your solutions and make sure to include
    the resulting data in your rendered document.
    -   Make sure to not print more than 10 rows of data (unless
        specifically instructed to).
-   Always submit both the rendered document(s) as well as your source
    Rmarkdown document. Submit the files separately on moodle, **not**
    as a zip archive.

## Exercise 1: Initializing git (4 Points)

For this whole exercise sheet we will be tracking all our changes to it
in git.

a)  Start by initializing a new R project with git support, called
    `exeRcise-sheet-3`. If you forgot how to do this, you can follow
    this
    [guide](https://malikaihle.github.io/Introduction-RStudio-Git-GitHub/rstudio_project.html).
b)  Commit the files generated by Rstudio.
c)  For all of the following tasks in this exercise sheet we ask you to
    always commit your changes after finishing each subtask e.g. create
    a commit after task *1d*, *1e* etc.

> Note: This applies only to answers that have text or code as their
> answer. If you complete tasks in a different order or forget to commit
> one, this is no problem. If you change your answers you can just
> create multiple commits to track the changes.

d)  Name 2 strengths and 2 weaknesses of git. (Don't forget to create a
    commit after this answer, see *1c*). 
  **-strength**.  
      Branching and Merging: Git provides powerful branching and merging capabilities. Developers can            create multiple branches to work on different features or experiments independently, and later merge       them back into the main codebase. This enables parallel development, isolation of changes, and             facilitates collaboration among team members.    
      Version Control: Git excels at managing versions of a project's source code. It tracks changes at a        granular level, allowing you to view the history of modifications, compare different versions, and         easily revert to a previous state if needed. This capability is particularly useful in collaborative       development environments.  
  **-weakness**.  
  Complexity with Advanced Features: While Git's core functionality is relatively straightforward, it        can become more complex when dealing with advanced features such as rebasing, resolving conflicts,         or handling submodules. These operations may require a deeper understanding of Git's internal              workings, and mistakes can potentially lead to data loss or confusion if not executed properly.  
  Steep Learning Curve: Git has a reputation for having a steep learning curve, especially for users         who are new to version control systems or have only worked with centralized systems in the past. The       command-line interface and the multitude of commands and options can be overwhelming for beginners.        However, there are also user-friendly Git clients available that provide graphical interfaces and          simplify the learning process. 

e)  Knit this exercise sheet. Some new files will automatically be
    generated when knitting the sheet e.g. the HTML page. Ignore these
    files, as we only want to track the source files themselves.

## Exercise 2: Putting your Repository on GitHub (3.5 Points)

For this task you will upload your solution to GitHub.

a)  Create a new repository on GitHub in your account named
    `exeRcise-sheet-3`. Make sure you create a **public repository** so
    we are able to see it for grading. Add the link to the repository
    below:
b)  Push your code to this new repository by copying and executing the
    snippet on github listed under
    `…or push an existing repository from the command line`.
c)  Regularly push your latest changes to GitHub again and especially do
    so when you are finished with this sheet.

## Exercise 3: Baby-Names in Munich (4.5 Points)

Download the latest open datasets on given names ("Vornamen") from the
open data repository of the city of Munich for the years `2022` and
`2021`.

Link: <https://opendata.muenchen.de/dataset/vornamen-von-neugeborenen>

a)  Download the data for both years and track it in git. For small
    datasets like these adding them to git is not a problem.
```{r}
vornamen_2021 <- read.csv("vornamen_2021.csv")
vornamen_2022 <- read.csv("vornamen_2022.csv")

```

b)  Load the data for both years into R. Check the type of the count
    variable ("Anzahl") and look into the data to determine why it is
    not numeric? Fix the problem in an appropriate manner, it is OK if
    some of the counts are inaccurate because of this. Explain your
    solution and the repercussions.  
-The Variable "Anzahl" is not  numeric, because the var "Anzahl" is abbreviated ,which has count of first name under 4. If the "Anzahl" has as Value '4 oder weniger', that Value is changed in a new  Variable "count" to 2, and  Variables "count" have now Data Type "Numeric".  
```{r}
library(tidyverse)
vornamen_2021 <- vornamen_2021 %>% mutate(count = ifelse(vornamen_2021$Anzahl=='4 oder weniger',2,vornamen_2021$Anzahl))
vornamen_2021$count <- as.numeric(vornamen_2021$count)
vornamen_2022 <- vornamen_2022 %>% mutate(count = ifelse(vornamen_2022$Anzahl=='4 oder weniger',2,vornamen_2022$Anzahl))
vornamen_2022$count <- as.numeric(vornamen_2022$count)
```

c)  Calculate the total number of babies born in Munich in 2022
    and 2021. Which year had the bigger baby-boom?  
    Year 2021 has bigger baby-boom then Year 2022. But the Values are not an exact Value ,because some Values in Column "Anzahl" are not pricise detemined,e.g "4 oder weniger". 

```{r}
total_babies_2021 <- sum(vornamen_2021$count)
total_babies_2022 <- sum(vornamen_2022$count)
```
    

d)  Add a new column `year` to both datasets which holds the correct
    year for each.
```{r}
vornamen_2021 <- vornamen_2021 %>% mutate(year=2021)
vornamen_2022 <- vornamen_2022 %>% mutate(year=2022)
```
e)  Combine both datasets into one using `bind_rows()`.
```{r}
df<-bind_rows(vornamen_2021,vornamen_2022)
```
f)  Combine the counts for same names to determine the most popular
    names across both years. Print out the top 10 names in a nicely
    formatted table for both years. Include a table caption.
```{r}
library(knitr)
popular_names <- df %>% group_by(Vorname) %>% summarize(total_count=sum(count))
popular_names <- popular_names %>%
  arrange(desc(total_count))
popular_names <- head(popular_names,10)
kable(popular_names,caption = "the top 10 names in 2021 and 2022")
```

## Exercise 4: Chat GPT + apply (3 points)

For this task: Specifically use ChatGPT to solve the task and submit
your prompts in addition to the solution

a)  The code below does not work because the wrong apply function has
    been used. Find out which apply function would be correct and why it
    did not work. Correct the code. Also calculate the rowwise means.
    
###Create a sample data frame

tax_data \<- data.frame( Name = c("Munich GmbH", "ABC Inc.", "Backpacks
1980", "Bavarian Circus"), Tax_2019 = c(5000, 4000, 6000, 3500),
Tax_2020 = c(4800, 4200, 5800, 3700), Tax_2021 = c(5200, 3800, 5900,
3400) )

###Calculate column-wise means

column_means \<- lapply(tax_data\[, -1\], 2, mean)

column_means
```{r}
##Create a sample data frame

tax_data <- data.frame( Name = c("Munich GmbH", "ABC Inc.", "Backpacks
1980", "Bavarian Circus"), Tax_2019 = c(5000, 4000, 6000, 3500),
Tax_2020 = c(4800, 4200, 5800, 3700), Tax_2021 = c(5200, 3800, 5900,
3400) )

# prompt : column_means <- lapply(tax_data[, -1], 2, mean) column_means
# right answer from Chat GPT 
# The code you provided calculates the mean value for each column of the "tax_data" data frame, excluding the first column. Here's a breakdown of the code:

#1. `tax_data[, -1]` selects all columns of the "tax_data" data frame except for the first column ("Name"). The comma (`,`) indicates that you want to select all rows.

#2. `lapply()` is a function in R that applies a given function to each element of a list or vector. In this case, it applies the `mean()` function to each column of the selected data frame.

#Therefore, the code `column_means <- lapply(tax_data[, -1], mean)` calculates the mean value for each column of the "tax_data" data frame, excluding the "Name" column, and stores the results in the "column_means" object. Each element of "column_means" corresponds to the mean value of a specific column in the "tax_data" data frame.
column_means <- lapply(tax_data[, -1], mean)
column_means
## prompt : calculate rowwise means
## answer from Chat Gpt
# Calculating row-wise means
row_means <- rowMeans(tax_data[, -1])

```
    



b)  Using ChatGPT try to understand what the rapply() function does.
    Create an easy example with mock data where the function is used and
    explain it in your words.
```{r}
# prompt: What is rapply() in R?
# explain from GPT: The rapply() function is particularly useful when dealing with complex nested structures, such as lists of lists, and you want to apply a function to each element in a recursive manner.
# example 
my_list <- list(a = 1:3, b = list(c = 4:6, d = 7:9))
result <- rapply(my_list, function(x) x * 2)
print(result)
# explain in our words: 
# list a has values 1,2,3 , so function(x) calculate x*2 , we get the result 2,4,6. And B is nested List.There is in list b two different Lists c and d. rapply() work as recursive, so the function go into list b to calculate , but list is nested, so function go into list c and calculates all values in c and then go to list d an calculate also all values in list d. And recursive in this function means , the function does not calculate this wise , e.g. b.c1 -> b.d1 ->  b.c2 -> b.d2 ...
```

## Final Note

Make sure to push all your commits and changes to GitHub before
submittining the exercise sheet.
